---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Loading Libraries
```{r echo=T}
library(dplyr)
library(tidyr)
library(ggplot2)
```
## 1. Code for reading in the dataset and/or processing the data

```{r}
activity_df =  read.csv(unz('activity.zip','activity.csv'))
activity_df$date = as.Date(activity_df$date)
bydate = na.omit(activity_df) %>% group_by(date)
byinterval = na.omit(activity_df) %>% group_by(interval)
```
## 2. Histogram of the total number of steps taken each day
```{r fig.height=4}
temp = bydate %>% summarise(sumsteps=sum(steps))
ggplot(temp,aes(sumsteps))+geom_histogram(bins=20)
```
## 3. Mean and median number of steps taken each day
```{r}
bydate %>% summarise(meansteps = mean(steps),mediansteps = median(steps))
```
## 4. Time series plot of the average number of steps taken
```{r fig.height=4}
temp = byinterval %>% summarise(meansteps=mean(steps))
ggplot(temp,aes(interval,meansteps))+geom_line()
```

## 5. The 5-minute interval that, on average, contains the maximum number of steps

```{r}
temp[which.max(temp$meansteps),]

```
## 6. Code to describe and show a strategy for imputing missing data

**total number of missing values in the dataset**
```{r}
apply(activity_df,2,function(x) sum(is.na(x)))
```

**imputed value is calculated by floor of average on each interval.**
```{r}
imputed_df = activity_df
imputed_val = byinterval %>% summarise(meanval = floor(mean(steps)))
for (i in 1:dim(activity_df)[[1]]){
  if(is.na(activity_df[i,'steps'])){
    imputed_df[i,'steps']=subset(imputed_val,interval==activity_df[i,'interval'])$meanval
  }
}
```

**median and mean of imputed df**
```{r}

imputed_df %>% group_by(date) %>%summarise(meansteps = mean(steps)
                                                     ,mediansteps = median(steps))
```
*The mean and median value by date is differ from the original data*

## 7. Histogram of the total number of steps taken each day after missing values are imputed
```{r fig.height=4}
imputed_bydate = imputed_df%>% group_by(date)
temp = imputed_bydate %>% summarise(sumsteps=sum(steps))
ggplot(temp,aes(sumsteps))+geom_histogram(bins=20)
```

## 8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}

imputed_df$day = weekdays(imputed_df$date)
imputed_df$weekend =as.factor(imputed_df$day=='Sunday' | imputed_df$day=='Saturday')
levels(imputed_df$weekend)<-c('Weekday','Weekend')
gpdata = imputed_df %>%
    group_by(interval,weekend) %>% 
    summarise(steps=mean(steps))
ggplot <-ggplot(data=gpdata,aes(x = interval,y=steps))
ggplot+geom_line()+facet_grid(rows =vars(weekend))
```

## 9. All of the R code needed to reproduce the results (numbers, plots, etc.) in the report
Here is the markdown file.
